\myTitle

### 2024-07-12 body-text-of-paper.tex
Update author contributions

We envision \gscramble{} to be relevant for a diverse range of potential applications. In our 
provided empirical examples with trout and wild pig data, we demonstrate the basics of 
creating hybrid classes. In much the same manner, \gscramble{} has been used to evaluate the statistical power 
of hybrid classification used to differentiate wild boar hybrids from domestic pigs 
\citep{smyser2024probgen}. Specifically \citet{smyser2024probgen} used the segregation options in \gscramble{} 
 to preserve founder individuals' genotypes in contrast to \textit{a priori} shuffling alleles 
within populations. This retains the subpopulation structure present within certain populations---thereby, better reflecting the 
actual admixture variation expected from wild boar and domestic pig hybrids. We think \gscramble{} 
may also be useful for assessing relatedness estimates using pedigrees of varying complexity. Here, it 
is important to note that each time a gamete is segregated in a GSP, its complement is also 
segregated---an example of antithetical variate sampling in Monte Carlo methods \citep{hammersley}.
Thus, in the  example of relatedness, fixed specified founders should be repeatedly ``mated'' with one offspring 
sampled per iteration to avoid sampling of anticorrelated genotypes.

>>>>

We envision \gscramble{} to be relevant for a diverse range of potential applications. In our 
provided empirical examples with trout and wild pig data, we demonstrate the basics of 
creating hybrid classes. In much the same manner, \gscramble{} has been used to evaluate the statistical power 
of hybrid classification used to differentiate wild boar hybrids from domestic pigs 
\citep{smyser2024probgen}. Specifically \citet{smyser2024probgen} used the segregation options in \gscramble{} 
 to preserve founder individuals' genotypes in contrast to \textit{a priori} shuffling alleles 
within populations. This retains the subpopulation structure present within certain populations---thereby, better reflecting the 
actual admixture variation expected from wild boar and domestic pig hybrids. We think \gscramble{} 
may also be useful for assessing relatedness estimates using pedigrees of varying complexity. Here, it 
is important to note that each time a gamete is segregated in a GSP, its complement is also 
segregated---an example of antithetical variate sampling in Monte Carlo methods \citep{hammersley}.
Thus, in the  example of relatedness, fixed specified founders should be repeatedly ``mated,'' with one offspring 
sampled per iteration to avoid sampling of anticorrelated genotypes.
